---
output: github_document
always_allow_html: yes
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```



# NOAA package 

This package contains following functions.

## eq_clean_data()
  It adds the column DATE and changes the type of LONGITUDE and LATITUDE columns. 
  It takes a dataframe with NOAA earthquake data as input and returns a dataframe with DATE column and it also changes the type of LONGITUDE and LATITUDE column to numeric.
```{r eq_clean_data, echo = TRUE, eval = TRUE, include = TRUE}
raw.noaa.df <- readr::read_tsv(system.file("extdata", "signif.txt", package = "NOAA"))
noaa.df <- NOAA::eq_clean_data(raw.noaa.df)
```
  
## eq_location_clean()
  It removes the country name from LOCATION_NAME column and also makes it Title case.
  This function makes an internal call to **eq_clean_data()** to ease the process. We could just call **eq_location_clean()** instead of calling both functions.
```{r eq_location_clean, echo = TRUE, eval = TRUE, include = TRUE}
raw.noaa.df <- readr::read_tsv(system.file("extdata", "signif.txt", package = "NOAA"))
noaa.df <- NOAA::eq_location_clean(raw.noaa.df)
```
  
## get_timeline()
  The wrapper function for geom_timeline. Renders the timeline based on countries parameter. 
  It takes the NOAA dataframe, a vector of countries and minimum and maximum values of timeline as input.
  It makes internal call to **geom_timeline()** and renders the output based on the value we give at "countries" attribute. 
  To render a timeline of earthquakes irrespective of countries we need to pass "*" in the countries parameter. 
```{r get_timeline, echo = TRUE, eval = TRUE, include = TRUE, fig.width = 8, fig.height = 4}
NOAA::get_timeline(noaa.df, "*","2000-01-01","2010-01-01")
NOAA::get_timeline(noaa.df, c("CHINA", "INDIA"),"2000-01-01","2010-01-01")
```
  For the output of get_timeline we could add the geom "geom_timeline_label()" which will add label to "n" number of earthquakes.
```{r geom_timeline_label, echo = TRUE, eval = TRUE, include = TRUE, fig.width = 8, fig.height = 4}
NOAA::get_timeline(noaa.df, c("CHINA", "INDIA"),"2000-01-01","2010-01-01") +
NOAA::geom_timeline_label(ggplot2::aes(x=DATE, location=LOCATION_NAME,xmin=xmin,xmax=xmax,size=EQ_PRIMARY,y=COUNTRY), n_max = 5)
```
## eq_map()
  It creates an interactive map with popup based on **annot_col** attribute.
  It takes the NOAA dataframe and annot_col value as input.
  The value of annot_col can be any column in the dataframe.
```{r eq_map, echo = TRUE, eval = TRUE, include = TRUE, fig.width = 8, fig.height = 4}
mexico.df <- dplyr::filter(noaa.df, COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000)
NOAA::eq_map(mexico.df, "DATE")
```
  
## eq_create_label()
  It creates a label with Location, Magnitude and Total Deaths.
```{r eq_create_label, echo = TRUE, eval = TRUE, include = TRUE, fig.width = 8, fig.height = 4}
mexico.df<- dplyr::mutate(mexico.df, popup_text = NOAA::eq_create_label(mexico.df))
NOAA::eq_map(mexico.df, "popup_text")
```

  
This package contains the following geoms.

## geom_timeline()
  A geom to render the timeline of earthquake with magnitude and total deaths.
  
## geom_timeline_label()
  A geom to add label to timeline of earthquake created by geom_timeline.
