---
title: "package_details"
author: "Gopal Seshadri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r global_options}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE, message = FALSE, warning = FALSE)
```

This package contains following functions.
## eq_clean_data()
  It adds the column DATE and changes the type of LONGITUDE and LATITUDE columns.
```{r eq_clean_data, echo = TRUE, eval = TRUE, include = TRUE}
raw.noaa.df <- readr::read_tsv(system.file("extdata", "signif.txt", package = "NOAA"))
noaa.df <- NOAA::eq_clean_data(raw.noaa.df)
str(noaa.df)
```
  
  
## eq_location_clean()
  It removes the country name from LOCATION_NAME column and makes it to title case. It also has an internal call to eq_clean_data().
```{r eq_location_clean, echo = TRUE, eval = TRUE, include = TRUE}
raw.noaa.df <- readr::read_tsv(system.file("extdata", "signif.txt", package = "NOAA"))
noaa.df <- NOAA::eq_location_clean(raw.noaa.df)
str(noaa.df)
```
  
  
## get_timeline()
  The wrapper function for geom_timeline. Renders the timeline based on countries parameter. Providing "*" to countries parameter returns a timeline without any country axis. On providing a vector of countries it will produce the timeline for only those countries.
```{r get_timeline, echo = TRUE, eval = TRUE, include = TRUE, fig.width = 8, fig.height = 4}
NOAA::get_timeline(noaa.df, "*","2000-01-01","2010-01-01")
NOAA::get_timeline(noaa.df, c("CHINA", "INDIA"),"2000-01-01","2010-01-01")
```
  For the output of get_timeline we could add the geom "geom_timeline_label()" which will add label to "n" number of earthquakes.
```{r geom_timeline_label, echo = TRUE, eval = TRUE, include = TRUE, fig.width = 8, fig.height = 4}
NOAA::get_timeline(noaa.df, c("CHINA", "INDIA"),"2000-01-01","2010-01-01") +
NOAA::geom_timeline_label(ggplot2::aes(x=DATE, location=LOCATION_NAME,xmin=xmin,xmax=xmax,size=EQ_PRIMARY,y=COUNTRY), n_max = 5)
```


## eq_map()
  It creates an interactive map with popup based on annot_col attribute.
```{r eq_map, echo = TRUE, eval = TRUE, include = TRUE, fig.width = 8, fig.height = 4}
mexico.df <- dplyr::filter(noaa.df, COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000)
NOAA::eq_map(mexico.df, "DATE")
```


## eq_create_label()
  It creates a label with Location, Magnitude and Total Deaths.
```{r eq_create_label, echo = TRUE, eval = TRUE, include = TRUE, fig.width = 8, fig.height = 4}
mexico.df<- dplyr::mutate(mexico.df, popup_text = NOAA::eq_create_label(mexico.df))
NOAA::eq_map(mexico.df, "popup_text")
```
  

